Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-08-20 Supplemental-Material-A-Annotated-Analysis.Rmd
Update Supplemental-Material-A-Annotated-Analysis.Rmd

The full ResponseId information with all relevant system information and all loaded and installed packages is available in the collapsible section below.

>>>>

The full session information with all relevant system information and all loaded and installed packages is available in the collapsible section below.
